Corpus Stats

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd

count_df <- read_rds("../data/final_loc_counts.RDS")
total_recorded_sigs <- read_rds("../data/final_recorded_sigs_by_package.RDS")

r_counts <- count_df[, 1]; names(r_counts) <- rownames(count_df)
c_counts <- count_df[, 2]; names(c_counts) <- rownames(count_df)

# for observations
records_by_fun <- readRDS("../data/final_obs_counts_df.RDS")
pkgs_to_plot <- intersect(rownames(records_by_fun), names(r_counts))

r_counts <- r_counts[pkgs_to_plot]
c_counts <- c_counts[pkgs_to_plot]
total_recorded_sigs <- total_recorded_sigs[pkgs_to_plot]

records_by_fun[ "pkg" ] <- rownames(records_by_fun) # needed for plotting
records_by_fun <- records_by_fun[records_by_fun[,"pkg"] %in% pkgs_to_plot, ]
records_by_fun$invo_rec <- unlist(total_recorded_sigs)

top_10 <- c("Rcpp", "rlang", "glue", "tibble", "stringi", "ggplot2", "dplyr", "pillar", "R6", "stringr")

# just named lists. some elements (in either) are integer(0) i believe, as some packages
# just have data.
```

@@

```{r}
r_c_df <- data.frame(package_name = names(r_counts), loc_r = r_counts)
# looks weird sorted
r_c_df_sub <- r_c_df[order(r_c_df$loc_r),]
# just get the entries with > 0 lines of code
r_c_df_sub <- r_c_df_sub[r_c_df_sub$loc_r > 0, ]
# looks weirder log10-scaled
r_c_df_sub$loc_r <- log10(r_c_df_sub$loc_r)

plot_r_counts <- ggplot( data=r_c_df_sub, aes(x=1:length(r_c_df_sub$loc_r), y=loc_r, group=1))
plot_r_counts <- plot_r_counts + geom_line() + geom_point()
plot_r_counts <- plot_r_counts + labs(
  title = "Analysis of R Corpus (R Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of R Code in Package (Log10-scaled)"
)

plot_r_counts <- plot_r_counts + theme(axis.text.x = element_blank())

# plot it
plot_r_counts

```

The outlier is the spatstat package.
How about for C?

```{r}
library(ggplot2)

c_c_df <- data.frame(package_name = names(c_counts), loc_c = c_counts)
# looks weird sorted
c_c_df_sub <- c_c_df[order(c_c_df$loc_c),]
# get rid of 0s
c_c_df_sub <- c_c_df_sub[c_c_df_sub$loc_c > 0, ]
# looks weirder log10-scaled
c_c_df_sub$loc_c <- log10(c_c_df_sub$loc_c)

plot_c_counts <- ggplot( data=c_c_df_sub, aes(x=1:length(c_c_df_sub$loc_c), y=loc_c, group=1))
plot_c_counts <- plot_c_counts + geom_line() + geom_point()
plot_c_counts <- plot_c_counts + labs(
  title = "Analysis of R Corpus (C Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of C Code in Package (Log10-scaled)"
)

plot_c_counts <- plot_c_counts + theme(axis.text.x = element_blank())

# plot it
plot_c_counts

```

Similar to the R stuff.
Now, we should combine these plots.
Messy graphs, beware!
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- - sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]
# this makes sure the package_names are in the right order, ggplot2 plots according to factors
# and levels
combo_df$package_name <- factor(combo_df$package_name, levels=combo_df$package_name)

loc_of_top_10 <- lapply(1:length(combo_df$package_name), function(x) if (combo_df$package_name[[x]] %in% top_10) x else FALSE)

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")
# zzz_c <- melt(combo_df_c, id.vars="package_name", variable.name = "language")

plot_both <- ggplot( data=zzz, aes(package_name, value, group=1))
plot_both <- plot_both + geom_line(aes(colour = language), size=0.05) # +  geom_point(aes(colour = language))
plot_both <- plot_both + labs(
  title = "Analysis of R Corpus (R and C)",
  y = "Lines of Code in Package (Log10-scaled)"
) + guides(colour=F)

# cut_top <- data.frame( x = c(-Inf, Inf), y = 2, cutoff = factor(2) )
# cut_bot <- data.frame( x = c(-Inf, Inf), y = -2, cutoff = factor(-2) )

plot_both <- plot_both + theme(
  axis.text.x  = element_blank(), 
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_line(), 
  panel.grid.major.y = element_line(colour = "red")) + # ,
  # panel.ontop = T) + 
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000)) +
  geom_text_repel(data=subset(zzz, package_name %in% top_10 & language == "loc_r"),
                  aes(y = 0, label=package_name), position=position_dodge(0.9), direction="y")
  # trying to get some text to show up

# plot it
plot_both

ggsave("../paper/plots/linesofrandccode.jpg", plot_both)

```

Plot:
```{r}

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
# records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))
# records_by_fun$invo_rec <- sapply(records_by_fun$invo_rec, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=invo_rec, y=invo_obs)) +
                geom_point(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Obs Invocations in Pkg",
                      x = "Rec Invocations in Pkg")
                # theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                #       axis.ticks.x=element_blank()) #+
                # scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6),
                #      labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))

# plot
plot_records

# generate file
ggsave("../paper/plots/recordsbypkg.jpg", plot_records)
```

>>>>

count_df <- read_rds("../data/final_loc_counts.RDS")
as.tibble(count_df) %>%
  mutate(names = rownames(count_df)) -> cloc

# for observations
t_r_s <- read_rds("../data/final_recorded_sigs_by_package.RDS")
tibble(names=names(t_r_s), rec = unlist(t_r_s)) -> total_recorded_sigs

r_b_f <- read_rds("../data/final_obs_counts_df.RDS")
as.tibble(r_b_f) %>%
  mutate(names = row.names(records_by_fun)) %>%
  rename(obs = invo_obs) %>%
  select(names, obs) -> records_by_fun

total_recorded_sigs %>%
  inner_join(records_by_fun, by="names") %>%
  filter(obs != 0, rec !=0) %>% 
  inner_join(cloc, by="names") %>%
  filter(r_counts != 0) -> df

top_10 <- c("Rcpp", "rlang", "glue", "tibble", "stringi", "ggplot2", "dplyr", "pillar", "R6", "stringr")
# just named lists. some elements (in either) are integer(0) i believe, as some packages
# just have data.
```

@@

```{r}
df %>%
  arrange(r_counts) %>%
  mutate(names_o = factor(names, names) , r_c_log= log10(r_counts), c_c_log = ifelse((c_counts==0),0, log10(c_counts)))  -> df_rc

df_rc %>% 
  ggplot(aes(x=names_o, y=r_c_log, group=1)) +
  geom_line() + geom_point() + labs(title = "Analysis of R Corpus (R Code Portion)",
    x = "Corpus of Analyzed Packages", 
    y = "Lines of R Code in Package (Log10-scaled)") + theme(axis.text.x = element_blank())
```

```{r}

df_rc %>% 
  ggplot(aes(x=names_o, y=c_c_log, group=1)) +
  geom_line() + geom_point() + labs(title = "Analysis of R Corpus (C Code Portion)",
    x = "Corpus of Analyzed Packages", 
    y = "Lines of C Code in Package (Log10-scaled)") + theme(axis.text.x = element_blank())
```

Similar to the R stuff.
Now, we should combine these plots.
Messy graphs, beware!
```{r}
loc_of_top_10 <- lapply(1:length(combo_df$package_name), function(x) if (combo_df$package_name[[x]] %in% top_10) x else FALSE)

df_rc %>% 
  select(names_o, r_c_log, c_c_log) %>% 
  mutate(c_c_log=-c_c_log) %>%
  melt(id.vars="names_o",variable.name="language") -> zzz

zzz %>%
ggplot(aes(x=names_o, value, group=1)) +
 geom_line(aes(colour = language), size=0.05) +
 labs(title = "Analysis of R Corpus (R and C)", y = "Lines of Code in Package (Log10-scaled)") + guides(colour=F) + 
 theme( axis.text.x  = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(),  panel.grid.major.y = element_line(colour = "red")) + # ,
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000))

#+  geom_text_repel(data=subset(zzz, names %in% top_10 & language == "loc_r"), 
#                  aes(y = 0, label=names), position=position_dodge(0.9), direction="y")

ggsave("../paper/plots/linesofrandccode.pdf")
```

Plot:
```{r}
df_rc %>%
  mutate(rec=log(rec),obs=log(obs))  %>%
  ggplot(aes(x=rec, y=obs)) +
                geom_point(size=0.1) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Obs Invocations in Pkg",
                      x = "Rec Invocations in Pkg")
                # theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                #       axis.ticks.x=element_blank()) #+
                # scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6),
                #      labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))

# generate file
ggsave("../paper/plots/recordsbypkg.pdf")
```
